Exploring Income Inequality Dynamics in Canada: A Geospatial and Temporal Analysis

### 2024-04-03 paper/paper.qmd
upload

\begin{equation}
Y_{ij} = \beta_{0} + \beta_{1}Year_{i} + \beta_{2}Province_{j}
\label{eq-Model2}
\end{equation}

@@

```{r}
#| echo: false
#| eval: false
#| warning: false
#| label: tbl-modelresults
#| tbl-cap: "Summary results for first model"

modelsummary(
  list(
    "Model 1" = first_model
  ),fmt = 2
)
```

```{r}
#| echo: false
#| eval: true
#| warning: false
#| label: tbl-modelresults2
#| tbl-cap: "Summary results for second model"

modelsummary(
  list(
    "Model 2" = second_model
  ),fmt = 2
)
```

@tbl-modelresults

>>>>

y_i|\mu_i, \sigma &\sim \text{Normal}(\mu_i, \sigma) \
\mu_i &= \beta_0 + \beta_1 \times \text{Year}_i + \beta_2 \times \text{Geographical Location}_i\
\beta_0 &\sim \text{Normal}(0, 2.5) \
\beta_1 &\sim \text{Normal}(0, 2.5) \
\beta_2 &\sim \text{Normal}(0, 2.5) \
\sigma &\sim \text{Exponential}(1)
\label{eq-Model2}
\end{align}

@@

```{r}
#| label: tbl-model1
#| tbl-cap: "Summary results for first model"
#| echo: false
#| eval: true
#| warning: false
#| message: false
library(rstanarm)

second_model<- 
  readRDS(file = here::here("models/model.rds"))

modelsummary::modelsummary(
  list(
    "Model 1" = first_model,
    "Model 2" = second_model
  ), statistic = "mad",
  fmt = 2
)

@tbl-model1
